\begin{bibsection}
\item R.N.\ Slaybaugh. ``Nuclear and Innovating the Clean Energy Landscape." French Nuclear Energy Society Young Generation Workshop. Video Meeting. 28 Sept.\ 2016. (invited)

%\item R.N.\ Slaybaugh. ``Nuclear and Innovating the Clean Energy Landscape." NorCal ANS Meeting. Berkeley, CA. 21 Sept.\ 2016. (invited)

%\item R.N.\ Slaybaugh. ``Nuclear and Innovating the Clean Energy Landscape." NorCal ANS Meeting. Berkeley, CA. 21 Sept. 2016. (invited)

\item R.N.\ Slaybaugh. ``Nuclear Innovation: Concept to Execution." PHYSOR 2016. Sun Valley, ID. 2 May 2016. (invited)

%\item R.N.\ Slaybaugh. ``The Opportunity of Global Nuclear Innovation." UC Berkeley NE Dept.\ Graduate Colloquium. Berkeley, CA. DATE??? 2016. (invited)

\item R.N.\ Slaybaugh. ``The Opportunity of Global Nuclear Innovation." 49th Japan Atomic Industrial Forum (JAIF) Annual Conference. Tokyo, Japan. 12 April 2016. (invited)

\item R.N.\ Slaybaugh. ``Exascaling Nuclear Innovation." Keynote speaker, Conference on Data Analysis 2016. Santa Fe, NM. 4 March 2016. (invited) 

\item R.N.\ Slaybaugh. ``Hybrid Transport Methods for Shielding Challenges." Idaho National Laboratory seminar. Idaho Falls, ID. 20 Nov.\ 2015. (invited) 

\item K.L.\ Rowland, R.N.\ Slaybaugh. ``Developments in the GPU-accelerated WARP Monte Carlo Neutron Transport Code." Workshop sur l'utilisation des acc\'{e}l\'{e}rateurs (GPUs, MICs) pour les simulations Monte-Carlo. \'{E}cole Polytechnique, Saclay, France. 10 July 2015. 

\item R.N.\ Slaybaugh, S.C.\ Wilson. ``Solving Shielding Challenges: Self-Shielding and Strong Anisotropies." Oak Ridge National Laboratory Summer Intern Series. Oak Ridge, TN. 11 Jun.\ 2015. (invited)

%\item K.L.\ Rowland, R.M.\ Bergmann, R.N.\ Slaybaugh, J.L.\ Vujic. "Implementing delta-tracking in a GPU-accelerated Monte Carlo neutron transport code." 2nd Frontiers in Computational Physics Conference: Energy Sciences. Zurich, Switzerland. 2-5 Jun.\ 2015.  

%\item R.N.\ Slaybaugh. ``Solving Shielding Challenges: Self-Shielding and Strong Anisotropies." University of Florida NE Dept.\ Graduate Colloquium. Gainesville, FL. 2 Apr.\ 2015. (invited)

\item R.N.\ Slaybaugh, T.M.\ Evans, and S.W.\ Mosher. ``Improved Hybrid Modeling of Used Fuel Storage Facilities." DOE-NE MPACT meeting. Oak Ridge, TN. 24-26 Mar.\ 2015. (invited)

%\item R.N.\ Slaybaugh. ``Academia Panel." WiSE O.N.E.: Theory Into Practice conference . Berkeley, CA. 14 Mar.\ 2015. (invited)

\item R.N.\ Slaybaugh. ``Hybrid Methods for Shielding Challenges: Self-Shielding and Strong Anisotropies." Colorado School of Mines NE Program Graduate Colloquium. Golden, Colorado. 7 Jan.\ 2015. (invited)

%\item Rachel Slaybaugh. ``Computational Science in the 'Real World'." Computer Science I and II, Baldwin Upper School. Bryn Mawr, PA. 10 and 11 Dec.\ 2014. (invited)

%\item R.N.\ Slaybaugh. ``PyNE and Nuclear Data: A Next Generation Tool." Sather Next Generation Nuclear Science Meeting. Lawrence Berkeley National Laboratory. 9 Dec.\ 2014. (invited)

%\item R.N.\ Slaybaugh. ``Advanced Approaches to High-Performance Computing in Nuclear: Applications to Non-Proliferation." MIIT Delegation Visit to BNRC. Berkeley, CA. 8 Dec.\ 2014. 

\item R.N.\ Slaybaugh. ``Computational Methods and Software Development in Nuclear Engineering Research." Tea at Berkeley Institute for Data Science. Berkeley, CA. 4 Dec.\ 2014. (invited)

%\item R.N.\ Slaybaugh. ``Transitions Panel" and ``Summary Roundtable." Expanding Potential: A workshop on navigating the hurdles faced by women in STEM. Berkeley, CA. 15 Nov.\ 2014. (invited)

\item R.N.\ Slaybaugh. ``The PyNE Software Library: A Framework for ENSDF?" Nuclear Data Week Meeting. Brookhaven National Laboratory. 6 Nov.\ 2014. 

%\item R.N.\ Slaybaugh. ``The PyNE Software Library: Why and How?" ANS Northern California Local Section Meeting. Alfred's Steakhouse, San Francisco, CA. 22 Oct.\ 2014. (invited)

%\item R.N.\ Slaybaugh. ``What's New in Academia Panel." U.S.\ Women In Nuclear Annual Meeting. Marriott Copley Place, Boston, MA. 29 July 2014. (invited)

%\item R.N.\ Slaybaugh. ``The Resonance Factor Method: Accelerating Monte Carlo in the Presence of Space and Energy Self-Shielding." CEA-Saclay Colloquium. Saclay, France. 26 June 2014.

\item R.N.\ Slaybaugh. ``The Resonance Factor Method: Accelerating Monte Carlo in the Presence of Space and Energy Self-Shielding." Reactor Physics Methods and Analysis Group Seminar. Areva Headquarters, Paris, France. 27 June 2014.

%\item R.N.\ Slaybaugh, T.M.\ Evans, P.P.H.\ Wilson, S.C.\ Wilson. ``Radiation Transport: Computational Methods and Real-World Use.'' UC Berkeley NE Dept.\ Graduate Colloquium. Berkeley, CA. 29 Oct.\ 2012. (invited)

\item R.N.\ Slaybaugh, T.M.\ Evans, P.P.H.\ Wilson, S.C.\ Wilson. ``Radiation Transport: Computational Methods and Real-World Use.'' NC State Univ.\ NE Dept.\ Graduate Colloquium. Raleigh, NC. 8 Nov.\ 2012. (invited)

\item R.N.\ Slaybaugh. ``Acceleration Methods for Massively Parallel Deterministic Transport." KAPL Employment Meeting. Niskayuna, NY. 30 Aug.\ 2011. (invited)

\item R.\ Slaybaugh, M.\ Arbidze, S. Lamichhane, D. O'Connor. ``An Evaluation of European Union Energy Policies." UW--Madison Center for World Affairs and the Global Economy Seminar. Madison, WI. 11 May 2011.

\item R.N.\ Slaybaugh. ``Krylov Methods and JFNK." UW\textemdash Madison Radiation Hydrodynamics Meeting. Madison, WI. 16 Dec.\ 2010. (invited)

\item R.N.\ Slaybaugh, T.M.\ Evans, G.G.\ Davidson. ``Parallel Algorithms for Fixed-Source and Eigenvalue Problems." 2010 SIAM Annual Meeting. Pittsburgh, PA. 12-16 July 2010.

%\item R.N.\ Slaybaugh. ``Variance Reduction in MC21 using Forward Adjoint Variance Reduction (FAVRE)." Naval Reactors\textemdash Shielding Video-conference. Pittsburgh, PA. Aug.\ 2010.

\item R.N.\ Slaybaugh. ``MC21\textemdash Jaguar Coupling for Variance Reduction." KAPL Physics Forum. Niskayuna, NY. July 2009.

\end{bibsection}


