%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume2} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Rachel N. Slaybaugh} % Your name
\address{Department of Nuclear Engineering \\ University of California, Berkeley} % Your address
\address{4173 Etcheverry Hall MC 1730 \\ Berkeley, CA 94720} % Your secondary addess (optional)
\address{(570)~$\cdot$~850~$\cdot$~3385 \\ slaybaugh@berkeley.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{tabbing}
Ph.D. \hspace*{2 em}\= \textbf{University of Wisconsin--Madison} \hspace*{5em} \= \hspace*{15em} \= 2011 \\
      \> Nuclear Engineering and Engineering Physics, with a certificate in \\ \> Energy Analysis and Policy \> GPA: 3.971\\
%
M.S. \hspace*{2 em}\> \textbf{University of Wisconsin--Madison} \> \> 2008 \\
      \> Nuclear Engineering and Engineering Physics \> GPA: 3.958\\
%
B.S. \hspace*{2 em}\> \textbf{Pennsylvania State University} \> \> 2006 \\
      \> Nuclear Engineering \> GPA: 3.67\\
\end{tabbing}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{University of California, Berkeley}{Jan.\ 2014 - Present}{Assistant Professor of Nuclear Engineering}{Berkeley, CA}
\item Researching transport methods for applications in safeguards and security, shield design, and reactor physics
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Bettis Laboratory}{Mar.\ 2012 - Aug.\ 2014}{Senior Engineer in the Shield Design and Development group}{West Mifflin, PA}
\item Implemented the Forward-Weighted Consistent Adjoint Driven Importance Sampling (FW-CADIS) method for variance reduction in Monte Carlo; accredited method for use in shield design
\item Developed new Resonance Factor variance reduction method for streaming through materials with space and energy self-shielding
\item Built two software tools in support of using FW-CADIS for shield design
\item Scientific Software Development Committee: leader in developing internal website for sharing software carpentry tools and resources
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of Wisconsin--Madison}{Sept.\ 2006 - Nov.\ 2011}{Research Assistant / Rickover Fellow}{Madison, WI}
\item Researched “Acceleration Methods for Massively Parallel Deterministic Transport”: added parallelization in the energy domain, an advanced eigenvalue solver, and a new multigrid in energy preconditioner to Denovo, developed at Oak Ridge National Lab
\item Investigated effects of uncertainty in gamma sources on Monte Carlo transport
\item Developed two Monte Carlo source sampling methods for arbitrarily shaped plasma sources; the sources are generated directly from plasma physics data
\item Wrote an efficient sampling method for secondary photon sources in the Monte Carlo CAD software library, Direct Accelerated Geometry Monte Carlo (DAGMC)
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Knolls Atomic Power Laboratory}{Summer 2009}{Rickover Fellow Practicum}{Schenectady, NY}
\item Helped couple the Monte Carlo code MC21 to the deterministic code Jaguar via the interface code UNIK for the purpose of variance reduction
\item Added weight window capability to MC21 
\item Investigated and recommended methods for creating weight window values 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Forschungszentrum Karlsruhe (KIT)}{May 2008 - Dec.\ 2008}{Visiting Researcher}{Karlsruhe, Germany}
\item Learned about the Rigorous 2 Step method for Monte Carlo geometry conversion while working in the Reactor Safety group
\item Helped group incorporate DAGMC library into MCNP workflow
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Oak Ridge National Laboratory}{Summers 2005 \& 2006}{Summer Intern}{Oak Ridge, TN}
\item Investigated use of the 3-D deterministic transport code TORT for radiation treatment planning (RTP) when using proper cross sections
\item Demonstrated that RTP is possible with TORT, but for limited cases
\item Learned about electron transport and created electron cross sections with CEPXS
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Penn State Breazeale Reactor}{Jan.\ 2003 - Apr.\ 2006}{Reactor Operator}{University Park, PA}
\item NRC licensed Reactor Operator for a TRIGA Mark III reactor
\item Analyzed core burn-up anomaly; calibrated gamma irradiation facilities
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{TEACHING Experience}

\begin{rSubsection}{University of California, Berkeley}{Jan.\ 2014 - Present}{Assistant Professor of Nuclear Engineering}{Berkeley, CA}
\item Taught NE 155, Introduction to Numerical Simulations for Radiation Transport, Spring 2014
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Software Carpentry Scientific Computing Workshop}{Apr. 14-15, 2014}{Instructor}{Berkeley, CA}
\item Hosted by Lawrence Berkeley National Laboratory
\item Introductory material, Version Control, Object Oriented Concepts in Python
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Bettis Laboratory}{Mar.\ 2012 - Aug.\ 2014}{Senior Engineer in the Shield Design and Development group}{West Mifflin, PA}
\item Qualified instructor for Bettis Reactor Engineering School (BRES), an internal school for new DOE-Naval Reactors employees
\item Co-taught BRES Shielding course Fall 2012, 2013 and Spring 2013
\item Used internally-written shielding text by R. Amato
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of Pittsburgh}{Fall 2012, Spring 2013}{Adjunct Professor}{Pittsburgh, PA}
\item Co-taught Introduction to Nuclear Engineering (ENGR 1700), which covers theory / basic nuclear engineering, basics of nuclear power reactors, and nuclear power reactor operations
\item Co-taught \textit{new} course Nuclear Chemistry and Radiochemistry (ENGR 2112, Spring): responsible for nuclear astrophysics and migration of radionuclides through the environment
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Virtual Science Challenge}{Apr.\ 2012-Mar.\ 2013}{Mentor}{Monterey, CA}
\item Mentor for winning U.S.\ team in international nuclear nonproliferation science fair, organized through the Center for Nonproliferation Studies
\item Facilitated online discussions, participated in workshops, and served as an information resource for the students throughout their project
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Penn State Breazeale Reactor}{Jan.\ 2003 - Apr.\ 2006}{Educational Outreach}{University Park, PA}
\item Taught Freshman Seminar and led tours for kindergarten through college students
\item Developed educational tools such as handouts, presentations, and games
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	SELECTED PRESENTATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Selected Presentations}

\begin{bibsection}
\item R.N.\ Slaybaugh, T.M.\ Evans, P.P.H.\ Wilson, S.C.\ Wilson. ``Radiation Transport: Computational Methods and Real-World Use.'' N.C.\ State Univ. NE Dept. Graduate Colloquium. Raleigh, NC. 8 Nov.\ 2012. (invited)

\item R.N.\ Slaybaugh. ``Acceleration Methods for Massively Parallel Deterministic Transport." KAPL Employment Meeting. Niskayuna, NY. 30 August 2011. (invited)

\item R.\ Slaybaugh, M.\ Arbidze, S. Lamichhane, D. O’Connor. ``An Evaluation of European Union Energy Policies." UW-Madison Center for World Affairs and the Global Economy Seminar. Madison, WI. 11 May 2011.

\item R.N.\ Slaybaugh. ``Krylov Methods and JFNK." UW-Madison Radiation Hydrodynamics Meeting. Madison, WI. 16 Dec 2010.

\item R.N.\ Slaybaugh, T.M.\ Evans, G.G.\ Davidson. ``Parallel Algorithms for Fixed-Source and Eigenvalue Problems." 2010 SIAM Annual Meeting. Pittsburgh, PA. 12-16 July 2010.

\item R.N.\ Slaybaugh. ``Variance Reduction in MC21 using Forward Adjoint Variance Reduction (FAVRE)." Naval Reactors – Shielding Video-conference. Pittsburgh, PA. August 2010.

\item R.N.\ Slaybaugh. ``MC21 – Jaguar Coupling for Variance Reduction." KAPL Physics Forum. Niskayuna, NY. July 2009.

\end{bibsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS AND AWARDS
%----------------------------------------------------------------------------------------
\vspace*{1em}
\begin{rSection}{Honors And Awards}

\begin{tabular}{ @{} l @{\hspace{6ex}} r }
American Nuclear Society (ANS) Presidential Citation & 2014 \\
Rickover Fellowship 	& 2008-2011 \\
Second Place, ANS Winter Meeting Poster Session	&2011\\
Modeling Experimentation and Validation (MeV) Reactor Physics School	& Jul.\ 2011\\
Selected to participate in Energy Hub conference Poster Session	&2011\\
Everitt P.\ Blizard Memorial Scholarship, ANS	&2010-2011\\
ANS Mathematics and Computation Division Best Summary + Presentation Award  &Nov.\ 2010\\
Graduate Scholarship, ANS 	&2009-2010\\
Selected Lindau Meeting of Nobel Laureates in Physics participant &	2008\\
Second Place, ANS Winter Meeting Poster Session	&Nov.\ 2007\\
Best Paper, Health Physics Track, ANS Student Conference 	&2007\\
Tau Beta Pi Honor Society	&2006\\
Alpha Nu Sigma Honor Society 	&2005 \\
Best Paper, Outreach and Education Track, ANS Student Conference	&2005
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Computer Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C++, Fortran 90/95/2003, Python, MATLAB \\
Version Control & git, svn, cvs \\
Test Frameworks & CTest, GoogleTest, nose \\
Tools & Doxygen, \LaTeX, MathCAD, Mathematica, MCNP, the shell, Vim, tcsh, bash, \\&Emacs, Trilinos, LAPACK, MPI, Valgrind
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SERVICE
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Service}

%------------------------------------------------
\textit{American Nuclear Society}, National Level
\begin{tabbing}
\hspace*{2 em}\= Math and Comp.\ Division \hspace*{6em} \= Exec.\ Comm.\ 2013-present \\
%
\> Nuclear Young Members Group \> Exec.\ Comm.\ 2014-present\\
%
\> NEED Comm.\ \> Chair 2013-present, Vice Chair 2010-2013\\
%
\> Professional Divisions Comm.\ \>	Vice chair 2012-present \\
%
\> Student Sections Comm.\ \> Chair 2010-2013, Vice Chair 2009-2010\\
%
\> Professional Women in ANS	\> Chair 2008-2010, Vice Chair 2006-2008\\	
%
\> Board of Directors \>	Student Member 2007-2009\\
%
%\> Conference suport \> PHYSOR 2014 reviewer, RPSD 2014 Session organizer \\
\> Other committee service \>	Membership, Bylaws and Rules, Public Info., 2013 \\ \> \> Nominating Comm., 2014 Special Selection Comm.\ \\ \> \> for Nominating Comm.\ Candidates
\end{tabbing}

%------------------------------------------------
\vspace*{-.5em}
\textit{Software and Computing}
\begin{tabbing}
\hspace*{2 em}\= The Hacker Within, UCB \hspace*{6em} \= Faculty Advisor 2014-present\\
\>(http://thehackerwithin.github.io/berkeley/)\\
%
\> Software Carpentry  \> Instructor since 2013\\
\> (http://software-carpentry.org/)\\
%
\> The Hacker Within, UW \> Bootcamp instructor 2009, Founding member 2009
\end{tabbing}

%------------------------------------------------
\textit{Energy and Science}
\begin{tabbing}
\hspace*{2 em}\= SIAM  \hspace*{15em} \= Member 2009-present\\
%
\> UCB--ANS \> Faculty co-Advisor 2014-present  \\
%
\> UW--SIAM \> Founding member 2009\\
%
\> Nuclear Engineering Student Delegation \> Co-Vice Chair 2010, Selected Participant 2009\\
%
\> UW--Energy Hub \> Conference Speaker Chair 2009, Founding Member 2007,  \\ \> \> liaison to Collegiate Energy Association 2008-2010\\
%
\> UW--Women In Nuclear \> President 2008-2009, Vice President 2006-2008,  \\ \> \> Founding Member 2006\\
%
\> UW--ANS \> Public Information Officer 2006-2007 \\
%
\> Fireside Society \> Judging advisor for Clean Tech Open competition 2011,  \\ \> \>Member 2011-present
\end{tabbing}

\end{rSection}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

\begin{bibsection}
\item S.C.\ Wilson and R.N.\ Slaybaugh. ``Improved Monte Carlo Variance Reduction for Space and Energy Self-Shielding," \textit{Nuclear Science and Engineering}. Accepted March 2014.

\item S.C.\ Wilson and R.N.\ Slaybaugh. ``Monte Carlo Importances in the Presence of Space and Energy Self-Shielding," Proceedings of the 2013 ANS Winter Meeting in Washington, DC, Nov 2013. Transactions vol.\ 109.

\item R.N.\ Slaybaugh, T.M.\ Evans, G.G.\ Davidson, and P.P.H.\ Wilson. ``Multigrid in energy preconditioner for Krylov solvers," \textit{Journal of Computational Physics}. \textbf{242} (2013) 405-419.

\item R.N.\ Slaybaugh and  S.C.\ Wilson. ``Deterministic Parameter Study for Fixed-Source Calculations Using FW-CADIS," Proceedings of the 2013 ANS Annual Meeting in Atlanta, GA, June 2013. Transactions vol.\ 108.

\item R.N.\ Slaybaugh, T.M.\ Evans, G.G.\ Davidson, and P.P.H.\ Wilson. ``Rayleigh Quotient Iteration in 3D, Deterministic Neutron Transport," Proceedings of the PHYSOR 2012 Meeting in Knoxville, TN, April 2012.

\item G.G.\ Davidson, T.M.\ Evans, J.J.\ Jarrell, R.N.\ Slaybaugh, and C.G.\ Baker, ``Massively Parallel, Three-Dimensional Transport Solutions for the k-Eigenvalue Problem," \textit{Nuclear Science and Engineering}. Accepted October 2013.

\item P.J.\ Snouffer, R.N.\ Slaybaugh, P.P.H.\ Wilson. ``Criticality Benchmark Comparisons for DAGMC," Proceedings of the 2011 ANS Annual Meeting in Hollywood, FL, June 2011. Transactions vol. 104.

\item T.M.\ Evans, A.S.\ Stafford, R.N.\ Slaybaugh, and K.T.\ Clarno. ``Denovo--A new three-dimensional parallel discrete ordinates code in SCALE." \textit{Nuc.\ Tech}. \textbf{171} (2010) 171-200.

\item G.G.\ Davidson, T.M.\ Evans, R.N.\ Slaybaugh, and C.G.\ Baker.  ``Massively Parallel Solutions to the k-Eigenvalue Problem," Proceedings of the 2010 ANS Winter Meeting in Las Vegas, NV, Nov 2010. Transactions vol.\ 103. [winner of Mathematics and Computation Division ``Best Summary + Presentation" award]

\item T.M. Evans, G.G. Davidson, and R.N. Slaybaugh.  ``Three-Dimensional Full Core Power Calculations for Pressurized Water Reactors," Proceedings of the 2010 Scientific Discovery through Advanced Computing (SciDAC) Conference. Chattanooga, TN, 11-15 July, 2010. Oak Ridge National Laboratory.

\item R.N.\ Slaybaugh, P.P.H.\ Wilson, L.A.\ El-Guebaly, and E.P.\ Marriott. ``Three-Dimensional Neutron Source Models for Toroidal Fusion Energy Systems." \textit{Fusion Engineering and Design}. \textbf{84} (2009) 1774-1778. 

\item R.N.\ Slaybaugh, ``Scouting Programs for Educational Outreach," Proceedings of the 2009 ANS Winter Meeting in Washington, DC, Nov 2009. Transactions vol.\ 101.

\item R.N.\ Slaybaugh, E.P.\ Marriott, P.P.H.\ Wilson, L.\ El-Guebal, ``A Study of the Effects of Source Sampling Methods on ARIES-RS NWL Profiles," Proceedings of the ARIES-Pathways Project Meeting, 28-29 May 2008, Madison WI. 

\item R.N.\ Slaybaugh, M.L.\ Williams, D.\ Ilas, D.E.\ Peplow, B.L.\ Kirk, T.L.\ Nichols, Y.Y.\ Azmy, and M.P.\ Langer, ``Radiation Treatment Planning Using Discrete Ordinates Codes," Proceedings of the 2007 ANS Annual Meeting in Boston, MA, June 2007. Transactions vol.\ 96.

\item R.\ Slaybaugh. ``Strengths and Weaknesses of Nuclear Engineering Education," presented at 2007 ANS Annual Meeting in Boston, MA, June 2007. Transactions vol.\ 96.
\end{bibsection}

\end{rSection}




%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
